Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | digital&nbsp;humanities&nbsp;instructor </font>

### 2023-06-27 cudan/paperplots.qmd
paper

plot.new()# just makes the spline work
fig_thematic = ggplot(pies2, aes(V1, V2))+
  geom_pie_glyph(radius=0.16, slices=attr(pies2, "mains"))+
  geom_point(aes(text=tool), data=ugenre %>% filter(type=="festival", ab=="A"), 
             size=0.5, fill=NA, alpha=0.9, color="black", shape=16)+
   geom_path(data=pies2 %>% ungroup %>%  filter(libelleFestival_NEW_VZ==exchange[1]) %>% select(V1, V2) %>% xspline(shape=-0.2, lwd=2, draw=F) %>% data.frame() %>% rename(V1=x,V2=y) , linewidth=0.5, arrow=arrow(angle=25, length=unit(0.06, "inch"), type="closed"), color="gray10", alpha=0.5)+
  #geom_point(aes(color=colorgenre), data=ugenre %>% filter(type=="film"), size=0.2, fill=NA,show.legend = FALSE)+
  geom_text_repel(aes(label=event,color=colorgenre, size=sizegen %>% log),
                  data=ugenre %>%
                    filter(type %in% c("genre", "film")) %>%
                    group_by(type) %>%
                    filter(type=="genre" | (type=="film" & ( (1:n()) %in% c(15,7, 8, 10, 23, 5)) ) )
                    #mutate(event=case_when(type=="film"~as.character(1:n()), T~type))
                    ,
            lineheight=0.55,
            alpha=0.9, hjust=1,
            bg.color=alpha("white", 0.7),
            show.legend = FALSE, max.overlaps=1000,
            box.padding = 0.2, point.padding = 10, min.segment.length = 999,
            force_pull=0.1,force=2,  max.time = 2)+
  scale_size(range=c(2.8,3.6), guide="none")+
  #scale_radius_manual(values=c(0.2, 0.14), guide="none")+
  #scale_shape_manual(values=abshapes, name="Festival\ntype")+

>>>>

plot.new()# just makes the spline work
fig_thematic = ggplot(pies2, aes(V1, V2))+
  geom_pie_glyph(radius=0.16, slices=attr(pies2, "mains"))+
  geom_point(aes(text=tool), data=ugenre %>% filter(type=="festival", ab=="A"), 
             size=0.5, fill=NA, alpha=0.9, color="black", shape=16)+
 geom_point(aes(text=tool), data=ugenre %>% filter(grepl("Goteborg", event)), size=3, stroke=1.1, fill=NA, alpha=0.9, color="black", shape=1)+
   #geom_path(data=pies2 %>% ungroup %>%  filter(libelleFestival_NEW_VZ==exchange[1]) %>% select(V1, V2) %>% xspline(shape=-0.2, lwd=2, draw=F) %>% data.frame() %>% rename(V1=x,V2=y) , linewidth=0.5, arrow=arrow(angle=25, length=unit(0.06, "inch"), type="closed"), color="gray10", alpha=0.5)+
  #geom_point(aes(color=colorgenre), data=ugenre %>% filter(type=="film"), size=0.2, fill=NA,show.legend = FALSE)+
  geom_text_repel(aes(label=event,color=colorgenre, size=sizegen %>% log),
                  data=ugenre %>%
                    filter(type %in% c("genre", "film")) %>%
                    group_by(type) %>%
                    filter(type=="genre" | (type=="film" & ( (1:n()) %in% c(15,7, 8, 10, 23, 5)) ) )
                    #mutate(event=case_when(type=="film"~as.character(1:n()), T~type))
                    ,
            lineheight=0.55,
            alpha=0.9, hjust=1,
            bg.color=alpha("white", 0.7),
            show.legend = FALSE, max.overlaps=1000,
            box.padding = 0.2, point.padding = 10, min.segment.length = 999,
            force_pull=0.1,force=2,  max.time = 2)+
  scale_size(range=c(2.8,3.6), guide="none")+
  #scale_radius_manual(values=c(0.2, 0.14), guide="none")+
  #scale_shape_manual(values=abshapes, name="Festival\ntype")+

### 2023-06-27 index.Rmd
paper

* Indrek Ibrus, Andres Karjus, Vejune Zemaityte, Ulrike Rohn, Maximilian Schich. 2022. Quantifying public value creation by public service media using big programming data | [socarxiv preprint](https://osf.io/preprints/socarxiv/hysma/)
* Andres Karjus, Christine Cuskley. 2022. Evolving linguistic divergence in socio-political polarities. Proceedings of the Joint Conference on Language Evolution (JCoLE). | [proceedings pdf](http://www.evolang.org/jcole2022_proceedings/jcole2022_proceedings.pdf) 
* Andres Karjus, Mar Canet Solà, Tillmann Ohm, Sebastian Ahnert, Maximilian Schich. 2022. Compression ensembles quantify aesthetic complexity and the evolution of visual art | [arxiv preprint](https://arxiv.org/abs/2205.10271) 
* Andres Karjus, Richard A. Blythe, Simon Kirby, Tianyu Wang, Kenny Smith. 2021. Conceptual similarity and communicative need shape colexification". [Cognitive Science](https://doi.org/10.1111/cogs.13035) (open access) | [pdf](https://andreskarjus.github.io/papers/Karjus_2021__Conceptual_Similarity_and_Communicative_Need_Shape_Colexification_An_Experimental_Study__Cognitive_Science.pdf) |  [bib](https://andreskarjus.github.io/bib/karjus_2021_cogsci.bib) | [code and data](https://github.com/andreskarjus/colexification_experiment)
* Andres Karjus, 2020. Competition, selection and communicative need in language change. PhD thesis, University of Edinburgh | [pdf](https://andreskarjus.github.io/thesis/Andres_Karjus_phd_thesis.pdf) | [1-page non-technical summary](https://andreskarjus.github.io/thesis/english_summary.pdf) | [eestikeelne lühikokkuvõte](https://andreskarjus.github.io/thesis/doktoritoo_ylevaade_AK.pdf)
*  Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith 2020. Communicative need modulates competition in language change | [preprint](https://arxiv.org/abs/2006.09277)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith 2020. Challenges in detecting evolutionary forces in language change using diachronic corpora. Glossa: a journal of general linguistics, 5(1), p.45. | [open access](http://doi.org/10.5334/gjgl.909) | [code](https://github.com/andreskarjus/wfsim_fit)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2020. Quantifying the dynamics of topical fluctuations in language. Language Dynamics and Change 10(1), 86-125 | [open access](https://doi.org/10.1163/22105832-01001200) | [code](https://github.com/andreskarjus/topical_cultural_advection_model)
* Andres Karjus, Martin Ehala, 2018. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change, 8, pp. 219-252 | [journal link](https://doi.org/10.1163/22105832-00802004) | [open postprint](Karjus_Ehala_2018_Testing_an_agent-based_model_of_language_choice_LDCpostprint.pdf) | <a href="karjus_testing_2018.bib" target="_blank">bib</a> | sociolinguistic [dataset](http://doi.org/10.15155/1-00-0000-0000-0000-00162L): 1000 respondents, 200 questions
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract, full paper above] | [open access](http://scholarworks.umass.edu/scil/) | <a href="karjus_topical_2018.bib" target="_blank">bib</a>
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [journal link](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency) | <a href="haspelmath_explaining_2017.bib" target="_blank">bib</a>

>>>>

* Andres Karjus, Mar Canet Solà, Tillmann Ohm, Sebastian Ahnert, Maximilian Schich. 2023. Compression ensembles quantify aesthetic complexity and the evolution of visual art. EPJ Data Science. 12, 21. | [open access](https://doi.org/10.1140/epjds/s13688-023-00397-3)
* Indrek Ibrus, Andres Karjus, Vejune Zemaityte, Ulrike Rohn, Maximilian Schich. 2022. Quantifying public value creation by public service media using big programming data | [socarxiv preprint](https://osf.io/preprints/socarxiv/hysma/)
* Andres Karjus, Christine Cuskley. 2022. Evolving linguistic divergence in socio-political polarities. Proceedings of the Joint Conference on Language Evolution (JCoLE). | [proceedings pdf](http://www.evolang.org/jcole2022_proceedings/jcole2022_proceedings.pdf) 
* Andres Karjus, Richard A. Blythe, Simon Kirby, Tianyu Wang, Kenny Smith. 2021. Conceptual similarity and communicative need shape colexification". [Cognitive Science](https://doi.org/10.1111/cogs.13035) (open access) | [pdf](https://andreskarjus.github.io/papers/Karjus_2021__Conceptual_Similarity_and_Communicative_Need_Shape_Colexification_An_Experimental_Study__Cognitive_Science.pdf) |  [bib](https://andreskarjus.github.io/bib/karjus_2021_cogsci.bib) | [code and data](https://github.com/andreskarjus/colexification_experiment)
* Andres Karjus, 2020. Competition, selection and communicative need in language change. PhD thesis, University of Edinburgh | [pdf](https://andreskarjus.github.io/thesis/Andres_Karjus_phd_thesis.pdf) | [1-page non-technical summary](https://andreskarjus.github.io/thesis/english_summary.pdf) | [eestikeelne lühikokkuvõte](https://andreskarjus.github.io/thesis/doktoritoo_ylevaade_AK.pdf)
*  Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith 2020. Communicative need modulates competition in language change | [preprint](https://arxiv.org/abs/2006.09277)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith 2020. Challenges in detecting evolutionary forces in language change using diachronic corpora. Glossa: a journal of general linguistics, 5(1), p.45. | [open access](http://doi.org/10.5334/gjgl.909) | [code](https://github.com/andreskarjus/wfsim_fit)
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2020. Quantifying the dynamics of topical fluctuations in language. Language Dynamics and Change 10(1), 86-125 | [open access](https://doi.org/10.1163/22105832-01001200) | [code](https://github.com/andreskarjus/topical_cultural_advection_model)
* Andres Karjus, Martin Ehala, 2018. Testing an agent based model of language choice on sociolinguistic survey data. Language Dynamics and Change, 8, pp. 219-252 | [journal link](https://doi.org/10.1163/22105832-00802004) | [open postprint](Karjus_Ehala_2018_Testing_an_agent-based_model_of_language_choice_LDCpostprint.pdf) | <a href="karjus_testing_2018.bib" target="_blank">bib</a> | sociolinguistic [dataset](http://doi.org/10.15155/1-00-0000-0000-0000-00162L): 1000 respondents, 200 questions
* Andres Karjus, Richard A. Blythe, Simon Kirby, Kenny Smith, 2018. Topical advection as a baseline model for diachronic lexical dynamics. Proceedings of The Society for Computation in Linguistics. Volume 1. [extended abstract, full paper above] | [open access](http://scholarworks.umass.edu/scil/) | <a href="karjus_topical_2018.bib" target="_blank">bib</a>
*	Martin Haspelmath, Andres Karjus, 2017. Explaining asymmetries in number marking: Singulatives, pluratives and usage frequency. Linguistics, volume 55, issue 6. | [journal link](https://www.degruyter.com/view/j/ling.2017.55.issue-6/ling-2017-0026/ling-2017-0026.xml)  | [preprint](https://www.academia.edu/25032500/Explaining_asymmetries_in_number_marking_Singulatives_pluratives_and_usage_frequency) | <a href="haspelmath_explaining_2017.bib" target="_blank">bib</a>
